Understanding the impacts of video-guided activities on parent-child interaction

### 2019-09-11 paper/manuscript.Rmd
finished bayesian regression changes

In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
There was also a significant main effect of age ($\beta=`r e2tja["age","beta"]`$, t(`r e2tja["age","df"]`) = `r e2tja["age","tval"]`, *p*=`r e2tja["age","pval"]`), showing that the number of episodes of JA decreased with the child's age. 
However, a significant interaction of age and condition ($\beta=`r e2tja["age:ConditionActivity Video","beta"]`$, t(`r e2tja["age:ConditionActivity Video","df"]`) = `r e2tja["age:ConditionActivity Video","tval"]`, *p*=`r e2tja["age:ConditionActivity Video","pval"]`), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.

@@

e2tja_age = ggplot(d, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() +
  ggthemes::theme_few()

@@

# Episodes of coordinated joint attention
cja_mod <- lmer(cja ~ age * Condition + (1 | video), data = e2ja,
                control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(cja_mod) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
e2cja <- get_lmer_reporting_values(cja_mod)
# also singular fit, convergence code: 0 - Bayesian regression confirms:
cja_bmod <- stan_glmer(cja ~ age * Condition + (1|video), data=e2ja)
summary(cja_bmod) # age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
#                                        mean    sd     2.5%   25%    50%    75%    97.5%
# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6

# Episodes of passive joint attention.
pja_mod <- lmer(pja ~ age * Condition + (1 | video), data = e2ja)
summary(pja_mod) # age beta=-2.88 t(13.4) = 2.53 p=.02
e2pja <- get_lmer_reporting_values(pja_mod)

# Total duration of passive joint attention.
pja_time_mod <- lmer(pja_length ~ age * Condition + (1 | video), data = e2ja,
                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(pja_time_mod) # singular - convergence code: 0, age beta=-18.89 t(80) = 2.72 p=.008
e2pja_time <- get_lmer_reporting_values(pja_time_mod)
pjat_bmod <- stan_glmer(pja_length ~ age * Condition + (1|video), data=e2ja)
summary(pjat_bmod) # age: est: -17.9 95% CI = [-33.1,-2.2]

# Total duration of coordinated joint attention.
cja_time_mod <- lmer(cja_length ~ age * condition + (1 | video), data = e2ja,
                     control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(cja_time_mod) # singular - convergence code: 0, marginal age: beta=37.35 t(80) = 1.95 p=.05
cjat_bmod <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
summary(cjat_bmod) # age: est: 35.3 95% CI = [-6.1,77.4] NOT SIGNIFICANT

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cja["ConditionActivity Video","beta"]`$, t(`r e2cja["ConditionActivity Video","df"]`) = `r e2cja["ConditionActivity Video","tval"]`, *p*=`r e2cja["ConditionActivity Video","pval"]`), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cja["age:ConditionActivity Video","beta"]`$, t(`r e2cja["age:ConditionActivity Video","df"]`) = `r e2cja["age:ConditionActivity Video","tval"]`, *p*=`r e2cja["age:ConditionActivity Video","pval"]`), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes revealed no significant effects.

In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["ConditionActivity Video","beta"]`$, t(`r e2pja["ConditionActivity Video","df"]`) = `r e2pja["ConditionActivity Video","tval"]`, *p*=`r e2pja["ConditionActivity Video","pval"]`), showing that older children had more episodes of passive JA with their caregiver.
The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pja_time["ConditionActivity Video","beta"]`$, t(`r e2pja_time["ConditionActivity Video","df"]`) = `r e2pja_time["ConditionActivity Video","tval"]`, *p*=`r e2pja_time["ConditionActivity Video","pval"]`), revealing that older children spent more time in passive JA with their caregiver.
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.

@@

#Episodes of coordinated joint attention
ms_cja <- d %>% group_by(Condition) %>%
  tidyboot_mean(cja)

e2cja <- ggplot(ms_cja, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of Coordinated JA") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")

e2cja_age = ggplot(d, aes(x = age, y = cja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
  langcog::scale_colour_solarized() + ggthemes::theme_few()

>>>>

In the regression predicting the number of episodes of JA, there was a significant main effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2tjaCond["95pLB"]`,`r e2tjaCond["95pUB"]`]), with more episodes of JA occurring after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
There was also a significant main effect of age ($\beta=`r e2tjaAge["age"]`$, 95% CI = [`r e2bidsAge["95pLB"]`,`r e2bidsAge["95pUB"]`]), showing that the number of episodes of JA decreased with the child's age. 
However, a significant interaction of age and condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2tjaAgeCond["95pLB"]`,`r e2tjaAgeCond["95pUB"]`]), shown in the right panel of Figure \ref{fig:e2ja}, demonstrates that older children in the Activity Video condition did not see a decrease in the number of episodes of JA.

@@

e2tja_age = ggplot(e2data, aes(x = age, y = total_ja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Total Episodes of Joint Attention") +
  langcog::scale_colour_solarized() +
  ggthemes::theme_few()

@@

# Episodes of coordinated joint attention
e2cja_m <- stan_lmer(cja ~ age * Condition + (1 | video), data = e2ja)
summary(e2cja_m) #  Condition: t(80) = 2.47 beta=1.37 p=.01; age*Condition beta=5.24 t(80) = 2.19 p=.02
e2cjaCond <- get_stan_glmer_reporting_values(e2cja_m, "ConditionActivity Video")
e2cjaAgeCond <- get_stan_glmer_reporting_values(e2cja_m, "age:ConditionActivity Video")
# age n.s., sig effect of condition: mean=1.3 95% CI=[.1,2.6]; age*condition mean=5.1 CI=[.5,9.6]
#                                        mean    sd     2.5%   25%    50%    75%    97.5%
# (Intercept)                             5.3    0.4    4.5    5.0    5.3    5.6    6.2 
# age                                    -2.0    1.4   -4.8   -2.9   -2.0   -1.1    0.9 
# ConditionVideo                          1.3    0.6    0.1    0.9    1.3    1.7    2.6 
# age:ConditionVideo                      5.1    2.3    0.5    3.5    5.1    6.5    9.6

# Episodes of passive joint attention.
e2pja_m <- stan_lmer(pja ~ age * Condition + (1 | video), data = e2ja)
summary(e2pja_m) # age beta=-2.7 95% CI=[-5.1,0.0]
e2pja <- get_stan_glmer_reporting_values(e2pja_m, "age")

# Total duration of passive joint attention.
e2pjat_m <- stan_lmer(pja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2pjat_m) # age: est: -17.9 95% CI = [-33.1,-2.2] 
e2pjat <- get_stan_glmer_reporting_values(e2pjat_m, "age")

# Total duration of coordinated joint attention.
e2cjat_m <- stan_glmer(cja_length ~ age * Condition + (1|video), data=e2ja)
summary(e2cjat_m) # age: est: 35.3 95% CI = [-6.1,77.4] ns

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the number of episodes of coordinated JA found a significant main effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, 95% CI = [`r e2cjaCond["95pLB"]`,`r e2cjaCond["95pUB"]`]), with more episodes of coordinated JA occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was no significant effect of age, but there was a significant interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, 95% CI = [`r e2cjaAgeCond["95pLB"]`,`r e2cjaAgeCond["95pUB"]`]), shown in Figure \ref{fig:e2ja-coord}, revealing that older children in the Activity Video condition had more episodes of coordinated JA than children in the Control Video condition.
The regression predicting the total duration of coordinated JA episodes revealed no significant effects.

In the regression predicting the number of episodes of passive JA, there was a main effect of age ($\beta=`r e2pja["age"]`$, 95% CI = [`r e2pja["95pLB"]`,`r e2pja["95pUB"]`]), showing that older children had more episodes of passive JA with their caregiver.
The regression predicting the total duration of passive JA revealed a main effect of age ($\beta=`r e2pjat["age"]`$, 95% CI = [`r e2pjat["95pLB"]`,`r e2pjat["95pUB"]`]), revealing that older children spent more time in passive JA with their caregiver.
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and suggest that the Activity Video strengthened this trend in the number of episodes of coordinated JA.

@@

#Episodes of coordinated joint attention
e2cjad <- e2ja %>% group_by(Condition) %>%
  tidyboot_mean(cja)

e2cja <- ggplot(e2cjad, aes(x = Condition, y = mean, fill = Condition)) + geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = position_dodge(width = .9)) +
  geom_point(data=d, aes(x=Condition, y=cja), alpha=.2, position = position_jitterdodge()) +
  xlab("Condition") + ylab("Episodes of Coordinated JA") +
  langcog::scale_fill_solarized() + ggthemes::theme_few() + theme(legend.position="none")

e2cja_age = ggplot(e2ja, aes(x = age, y = cja, group=Condition, colour = Condition)) +
  geom_point(alpha=.7) + geom_smooth(method='lm') + 
  xlab("Age (years)") + ylab("Episodes of Coordinated JA") +
  langcog::scale_colour_solarized() + ggthemes::theme_few()
